Miniproject - Combinatorics

### 2021-12-15 Combinatorics/submission.tex
small fixed, mainly to ANT

    Now consider a chain $C'_i$ from the assumption.
    Note that by Lemma~\ref{prop:properties_n_distribution_subsets}, we see that for $(n_0, ..., n_k) \in C'_i$ have
    \begin{itemize}
        \item Every element in $P(n_0, ..., n_k)$ is covered by $n_\delta$ elements
        \item Every element in $P(n_0, ..., n_k)$ covers $n_{\delta + 1}$ elements
    \end{itemize}
    The $P(n_0, ..., n_k)$ are exactly the layers of the poset $P'_i := \bigcup_{c \in C'_i} P(c)$.
    Hence Prop.~\ref{prop:biregular_implies_lym} yields that there is a sequence of maximal chains
    \begin{equation*}
        C_{i, 1}, ..., C_{i, t_i}
    \end{equation*}
    in the poset $P'_i$ such that each element in $P(n_0, ..., n_k)$ is contained in $t_i/|P(n_0, ..., n_k)|$ of them.
    Note that $R(C_{i, j}) := \{ R(x) \ | \ x \in C_{i, j} \} = C'_i$ holds.

@@

    Then the assumption of Prop.~\ref{prop:core_of_multisets} is fulfilled for $L_{l - 1} \cup L_l$.
    In particular, if this holds for all $0 < l \leq kd$ then the assumption is fulfilled for the whole of $\mathcal{C}_{k, d}$ and it follows that $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
\end{lemma}
\begin{proof}
    Exactly as in Lemma~\ref{prop:lp_algorithm}.
\end{proof}
Using a simple implementation of this approach, I could check that for some arbitrarily chosen values of $k, d$ up to $(k, d) = (8, 9)$, the poset $\mathcal{P}_{k, d}$ indeed satisfies the conditions of Prop.~\ref{prop:characterization_lym}.

>>>>

    Now consider a chain $C'_i$ from the assumption.
    Note that by Lemma~\ref{prop:properties_n_distribution_subsets}, we see that for $(n_0, ..., n_k) \in C'_i$ have
    \begin{itemize}
        \item Every element in $P(n_0, ..., n_k)$ is covered by $n_\delta$ elements in $P'_i$
        \item Every element in $P(n_0, ..., n_k)$ covers $n_{\delta + 1}$ elements in $P'_i$
    \end{itemize}
    where $P'_i \subseteq P$ is the graded poset that is given by the preimage of $C'_i$ under the canonical map $\mathcal{P}_{k, d} \to \mathcal{C}_{k, d}$, i.e.
    \begin{equation*}
        P'_i := \bigcup_{c \in C'_i} P(c) = R^{-1}(C'_i)
    \end{equation*}
    The $P(n_0, ..., n_k)$ are exactly the layers of the poset $P'_i$.
    Hence Prop.~\ref{prop:biregular_implies_lym} yields that there is a sequence of maximal chains
    \begin{equation*}
        C_{i, 1}, ..., C_{i, t_i}
    \end{equation*}
    in the poset $P'_i$ such that each element in $P(n_0, ..., n_k)$ is contained in $t_i/|P(n_0, ..., n_k)|$ of them.
    Note that $R(C_{i, j}) := \{ R(x) \ | \ x \in C_{i, j} \} = C'_i$ holds.

@@

    Then the assumption of Prop.~\ref{prop:core_of_multisets} is fulfilled for $L_{l - 1} \cup L_l$.
    In particular, if this holds for all $0 < l \leq kd$ then the assumption is fulfilled for the whole of $\mathcal{C}_{k, d}$ and it follows that $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
\end{lemma}
\begin{proof}
    Exactly as in Lemma~\ref{prop:lp_algorithm}.
\end{proof}
Using a simple implementation of this approach, I could check that for some arbitrarily chosen values of $k, d$ up to $(k, d) = (8, 9)$, the poset $\mathcal{P}_{k, d}$ indeed satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
Note that for this choice of $k, d$ we already have that $|\mathcal{P}_{8, 9}| = 134217728$ which is absolutely infeasible for more naive approaches.
